Lab2

### 2021-07-29 src/data/DataCleaning.Rmd
merged interim dataframe

```{r filter parameters, echo=FALSE}
# state(s) under investigation
state_id = c("TX","Texas")

@@

# cleaning
d_trips <- d_trips %>%
  # clean county name format
  mutate(
    County.Name = gsub("([A-Za-z]+).*", "\\1", County.Name),
    total_pop = select(.,Population.Staying.at.Home:Population.Not.Staying.at.Home) %>% rowSums(na.rm = TRUE)
    ) %>%
  group_by(County.FIPS) %>%
  mutate(
    # define long trips
    long_trip = sum(c_across(Number.of.Trips.100.250:Number.of.Trips...500)),
    long_trip_pc = long_trip/total_pop,
    # define short trips
    short_trip = sum(c_across(Number.of.Trips.1.3:Number.of.Trips.50.100)),
    short_trip_pc = short_trip/total_pop
  ) %>%
  rename(
    state = State.Postal.Code,
    county = County.Name
  ) %>%
  select(
    county, County.FIPS, state, total_pop, long_trip, long_trip_pc, short_trip, short_trip_pc
  ) %>%
  distinct(County.FIPS, .keep_all = TRUE)
```

```{r merged dataframe, echo=FALSE}
#code to merge state info to d
d <- merge(x = trips_col, y = covid_col, by = "county")
d <- merge(x = d, y = d_trips[ , c("county", "State.Postal.Code")], by = "county", all.x=TRUE)

#merge county policies to d
d_openings$strict <- d_openings$Closed.bars.x2 != "0"

d_openings$State.Postal.Code <- d_openings$State.Abbreviation
d <- merge(x = d, y = d_openings[ , c("State.Postal.Code", "strict")], by = "State.Postal.Code", all.x = TRUE)

#drop na and duplicates
d <- d %>% drop_na()
d <- unique(d)
```

>>>>

```{r filter parameters, echo=FALSE}
# state(s) under investigation
state_id = c("TX","Texas",48)

@@

# cleaning
d_trips <- d_trips %>%
  # clean county name format
  mutate(
    County.Name = gsub("([A-Za-z]+).*", "\\1", County.Name),
    total_pop = select(.,Population.Staying.at.Home:Population.Not.Staying.at.Home) %>% rowSums(na.rm = TRUE)
    ) %>%
  group_by(County.FIPS) %>%
  mutate(
    # define long trips
    long_trip = sum(c_across(Number.of.Trips.100.250:Number.of.Trips...500)),
    long_trip_pc = long_trip/total_pop,
    # define short trips
    short_trip = sum(c_across(Number.of.Trips.1.3:Number.of.Trips.50.100)),
    short_trip_pc = short_trip/total_pop
  ) %>%
  rename(
    state = State.Postal.Code,
    county = County.Name,
    fips = County.FIPS
  ) %>%
  select(
    county, fips, state, total_pop, long_trip, long_trip_pc, short_trip, short_trip_pc
  ) %>%
  distinct(fips, .keep_all = TRUE)
```

```{r merged dataframe, echo=FALSE}
#code to merge county info to d
d <- merge(x = d_trips, y = d_covid, by = "fips")

#drop na and duplicates
d <- d %>% drop_na()
d <- unique(d)

#merge county policies to d
# d_openings$strict <- d_openings$Closed.bars.x2 != "0"

# d_openings$State.Postal.Code <- d_openings$State.Abbreviation
# d <- merge(x = d, y = d_openings[ , c("State.Postal.Code", "strict")], by = "State.Postal.Code", all.x = TRUE)
```
```{r export interim dataframe as csv, echo=FALSE}

```
